Report and Figures

### 2016-06-23 5_figs.Rmd
minor adjustments due to compx refactor

---
title: "Report and Figures"
author: "Phil Chodrow"
date: "June 15, 2016"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: flatly
---

@@

library(compx)
library(ggplot2)
library(rgdal)
library(ggmap)
library(dplyr)
library(gridExtra)
library(readr)
library(ggrepel)
library(DT)
library(caTools)
library(tidyr)

@@

loss_curves <- read_csv('throughput/loss_curves.csv')
info_summary <- read_csv('throughput/info_cache.csv')

@@

cluster_map <- function(city){
	tracts <- readOGR(dsn = paste0('data/cities/',city), layer = 'geo', verbose = FALSE)
	tracts <- tracts[sum(tracts@data[,columns]) != 0,]
	clusters <- readRDS(paste0('throughput/clusterings/', city))

	tracts@data$cluster <- cutree(clusters,10)

@@

	to_plot <- fortify(tracts)

@@

	to_plot %>% 
		ggplot(aes(x = long, y = lat, group = id, fill = cluster)) +
		geom_polygon() + 
		scale_fill_distiller(palette = 'Set3', guide = FALSE) + 
		ggtitle(paste0('Example clustering for ', city)) + 
		theme_minimal() + 
		theme(axis.ticks = element_blank(),
			  axis.text = element_blank(),
			  axis.title = element_blank(),
			  panel.grid = element_blank())

@@

cluster_map('Detroit')

@@

make_cluster_groups <- function(city){
	tracts <- readOGR(dsn = paste0('data/cities/',city), layer = 'geo', verbose = FALSE)
	tracts <- tracts[sum(tracts@data[,columns]) != 0,]
	clusters <- readRDS(paste0('throughput/clusterings/', city))

	tracts@data$cluster <- cutree(clusters,10)

	I = mutual_info(tracts@data[,c(columns, 'cluster')])

@@

	tracts@data[,c(columns, 'cluster')] %>% 
		group_by(cluster) %>% 
		summarise_each(funs(sum)) %>%
		gather(key = race, value = n, -cluster) %>% 
		# group_by(cluster) %>% 
		mutate(n = n / sum(n)) %>% 
		ungroup() %>% 
		spread(key = race, value = n, fill = 0) %>% 
		arrange(desc(White)) %>% 
		mutate(cluster = factor(1:10, levels = 1:10)) %>%  
		gather(key = race, value = p, -cluster) %>% 
		mutate(city = city,
			   I = I,
			   title = paste0(city, ": I(C,Y) = ", round(I,2)))

@@

df <- rbind(make_cluster_groups('Detroit'), 
	  make_cluster_groups('Boston'),
	  make_cluster_groups('Dallas'),
	  make_cluster_groups('Atlanta'))

@@

loss_curves %>% 
	ggplot() +
	aes(x = nclust, y = I_XY, group = city) +
	geom_path(aes(color = weighted_J)) +
	geom_point(aes(color = weighted_J), size = .3) +
	scale_x_continuous(trans = 'log10', limits = c(1, max(loss_curves$nclust) + 1000)) +
	# scale_y_continuous(trans = 'log10') +
	geom_text(aes(x = nclust, y = I_XY, label = city, hjust = -.2), data = end_points) +
	theme_minimal() +
	scale_color_continuous(low = 'white', high = 'firebrick',limits = c(0,2)) +
	annotation_logticks(size = .1, sides = 'b') +
	ggtitle('Loss curves for spatially-constrained information-theoretic clustering')

>>>>

---
title: "Report and Figures"
author: "Phil Chodrow"
date: "June 15, 2016"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: simplex
---

@@

library(compx)
library(ggplot2)
library(rgdal)
library(ggmap)
library(dplyr)
library(gridExtra)
library(readr)
library(ggrepel)
library(DT)
library(caTools)
library(tidyr)
library(maptools)

@@

loss_curves <- read_csv('throughput/loss_curves.csv') %>% 
	group_by(city) %>% 
	arrange(desc(I_XY)) %>% 
	mutate(I_XY = max(I_XY) - I_XY,
		   nclust = row_number())

info_summary <- read_csv('throughput/info_cache.csv')

@@

cluster_map <- function(city, nclusters = 10){
	tracts <- readOGR(dsn = paste0('data/cities/',city), layer = 'geo', verbose = FALSE)
	tracts <- tracts[sum(tracts@data[,columns]) != 0,]
	clusters <- readRDS(paste0('throughput/clusterings/', city))

	tracts@data$cluster <- cutree(clusters,nclusters)
	overlay <- unionSpatialPolygons(tracts, IDs = tracts@data$cluster)

@@

	to_plot <- fortify(tracts)
	to_overlay <- fortify(overlay)

@@

	to_plot %>% 
		ggplot() +
		geom_polygon(aes(x = long, y = lat, group = group, fill = cluster)) + 
		scale_fill_distiller(palette = 'Set3', guide = FALSE) + 
		ggtitle(paste0('Example clustering for ', city)) + 
		theme_minimal() +
		theme(axis.ticks = element_blank(),
			  axis.text = element_blank(),
			  axis.title = element_blank(),
			  panel.grid = element_blank()) +
		geom_polygon(aes(x = long, y= lat, group = group), data = to_overlay, fill = NA, size = .3, color = 'white')

@@

cluster_map('Chicago', nclusters = 10)

@@

```{r fig.cap='Example clusterings for 4 major cities.'}

make_cluster_groups <- function(city, nclusters = 10){
	tracts <- readOGR(dsn = paste0('data/cities/',city), layer = 'geo', verbose = FALSE)
	tracts <- tracts[sum(tracts@data[,columns]) != 0,]
	clusters <- readRDS(paste0('throughput/clusterings/', city))

	tracts@data$cluster <- cutree(clusters,nclusters)

	I <- mutual_info(tracts@data[,c(columns, 'cluster')],group_col = 'cluster')

@@

	tracts@data[,c(columns, 'cluster')] %>% 
		group_by(cluster) %>% 
		summarise_each(funs(sum)) %>%
		gather(key = race, value = n, -cluster) %>% 
		# group_by(cluster) %>% 
		mutate(n = n / sum(n)) %>% 
		ungroup() %>% 
		spread(key = race, value = n, fill = 0) %>% 
		arrange(desc(White)) %>% 
		mutate(cluster = factor(1:nclusters, levels = 1:nclusters)) %>%  
		gather(key = race, value = p, -cluster) %>% 
		mutate(city = city,
			   I = I,
			   title = paste0(city, ": I(C,Y) = ", round(I,2)))

@@

nclusters = 5
df <- rbind(make_cluster_groups('Detroit', 3), 
	  make_cluster_groups('Boston', 5),
	  make_cluster_groups('Chicago', 4),
	  make_cluster_groups('Atlanta', 2))

@@

loss_curves %>% 
	ggplot() +
	aes(x = nclust, y = I_XY, group = city) +
	geom_path(aes(color = weighted_J)) +
	# geom_point(aes(color = weighted_J), size = .3) +
	scale_x_continuous(trans = 'log10', limits = c(1, max(loss_curves$nclust) + 1000)) +
	# scale_y_continuous(trans = 'log10') +
	geom_text(aes(x = nclust, y = I_XY, label = city, hjust = -.2), data = end_points) +
	theme_minimal() +
	scale_color_continuous(low = 'white', high = 'firebrick',limits = c(0,2)) +
	annotation_logticks(size = .1, sides = 'b') +
	ggtitle('Loss curves for spatially-constrained information-theoretic clustering')
